%-------------------------
% Resume in Latex
% Based off of : https://github.com/sb2nov/resume/
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\input{preamble.tex}
\input{macros.tex}

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{{\LARGE Neo Lee}} \\
  \href{mailto:neo.lky@berkeley.edu}{neo.lky@berkeley.edu} $\vert$
  \href{tel:+12137130311}{(213) 713-0311} $\vert$
  \href{https://github.com/moneybabe}{github.com/moneybabe}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \headstart
    \titleplacehead
      {University of California, Berkeley}{GPA: 4.0/4.0}
    \roletimehead
      {Bachelor of Arts, Applied Mathematics, Computer Science}{Graduation: 2025}
    \vspace{2pt}
    \listitem{Cal Alumni Leadership Scholarship}
    \vspace{5pt}
    \itemdesc{Relevant Coursework}{
      Data Structures and Algorithms,
      Functional Programming,
      Object Oriented Programming,
      Computer Architecture,
      Graph Theory,
      Cryptography,
      Discrete Mathematics,
      Probability Theory,
      Linear Algebra
    }
  \headend

%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
  \headstart
  \vspace{2pt}
    \itemdesc{Languages}{
      Python, C++, Java, SQL, MATLAB, R, Javascript, HTML, CSS, \LaTeX
    }
    \vspace{3pt}
    \itemdesc{Tools}{
      Pytorch, Sklearn, Pandas, Numpy, Matplotlib, MySQL, Selenium, BeautifulSoup, Git, Bash, Vim, 
      Figma
    }
  \headend

%-----------EXPERIENCE-----------------
\section{Experience}
  \headstart

    \titleplacehead
      {UC Berkeley Department of Mathematics}{Berkeley, CA}
      \roletimehead
        {Undergraduate Researcher - Mechanistic Interpretability}{September 2023 - Present}
        \itemstart
          \listitem{
            Reverse engineering the algorithms learned by neural network based chess engines using 
            Pytorch.
          }
          \listitem{
            Built an Alpha-beta pruning algorithm \& NN based chess engine with Python to study 
            the effect of neural network based evaluation functions on the performance of the 
            algorithm.
          }
        \itemend

      \roletimehead
        {Undergraduate Researcher - Stake-governed Random Turn Games}{August 2023 - Present}
        \itemstart
          \listitem{
            Built a finite integer line tug-of-war game simulator with Python to solve for Markov 
            perfect equilibria with dynamic programming, and visualized the results with Matplotlib.
          }
          \listitem{
            Constructed a computer assisted proof for the sufficient and necessary conditions for
            the existence of a Markov perfect equilibrium in infinite integer line tug-of-war games.
          }
        \itemend

    \titleplacehead
      {UC Berkeley Department of EECS}{Berkeley, CA}
      \roletimehead{Academic Tutor - CS61A}{August 2023 - Present}
        \itemstart
          \listitem{
            Tutored students in Functional Programming, Object Oriented Programming, 
            and Dynamic Programming with Python in lab sessions.
          }
          \listitem{
            Held weekly office hours to help students with homework and projects, and tutored 
            other tutors.
          }
        \itemend
  \headend


%-----------PROJECTS-----------------
\section{Projects}
  \headstart
    \titletimehead{Mathematical Error Analysis Library}{December 2023 - Present}
      \itemstart
        \listitem{
          Inspired by Pytorch and Numpy, I am building a Python library to perform arithmetic
          operations object-orientedly with associated error bounds factoring in floating point 
          error.
        }
        \listitem{
          Can be used in rigorous computer assisted proofs to bound the error of the results of
          mathematical expressions.
        }
      \itemend
    
    \titletimehead{2D Tile-based World Exploration Engine}{November 2023 (2 days)}
      \itemstart
        \listitem{
          Built a 2D tile-based world exploration engine with Java that generates a random world 
          with rooms and corridors, and allows the user to explore the world with a character.
        }
        \listitem{
          Implemented the A* search algorithm with Python to find the shortest path between two
          points in the world.
        }
        \listitem{
          Implemented a snake game with Java to allow the user to play the minigame in the world.
        }
      \itemend

    \titletimehead{Trading Bot}{June 2023 - August 2023}
      \itemstart
        \listitem{
          Implemented different machine learning models with Pytorch and Sklearn to predict the 
          price of cryptocurrency, e.g. LSTM, ARIMA, Linear Regression, Random Forest, 
          Sentiment Analysis, Transformer.
        }
        \listitem{
          Built a trading bot with Python to trade cryptocurrency on Bybit using the Bybit API.
        }
        \listitem{
          Implemented a backtesting framework with Python to test the performance of the trading 
          bot.
        }
      \itemend

    \titletimehead{Interview Questions Scraper}{April 2023 (1 hour)}
      \itemstart
        \listitem{
          Built a web scraper with Python and Selenium to scrape interview questions from 
          Glassdoor.
        }
      \itemend
  \headend

\end{document}
