%-------------------------
% Resume in Latex
% Based off of : https://github.com/sb2nov/resume/
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\input{preamble.tex}
\input{macros.tex}

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{{\LARGE Neo Lee}} \\
  \href{mailto:neo.lky852@gmail.com}{neo.lky852@gmail.com} $\vert$
  \href{tel:+12137130311}{(213) 713-0311} $\vert$
  \href{https://github.com/moneybabe}{github.com/moneybabe}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \headstart
    \titleplacehead
      {University of California, Berkeley}{GPA: 4.0/4.0}
    \roletimehead
      {Bachelor of Arts, Applied Mathematics, Computer Science}{Graduation: Spring 2025}
    \vspace{2pt}
    \listitem{Cal Alumni Leadership Scholarship}
    \vspace{5pt}
    \itemdesc{Mathematics Coursework}{
      Real Analysis,
      Complex Analysis,
      Topology,
      Algebra,
      Linear Algebra,
      Probability Theory,
      Stochastic Processes,
      Mathematical Statistics,
      Time Series Analysis,
      Graph Theory,
      Numerical Analysis,
      Discrete Mathematics,
      Cryptography
    }
    \itemdesc{Computer Science Coursework}{
      Optimization Theory,
      Machine Learning,
      Deep Learning,
      Efficient Algorithms,
      Functional Programming,
      Object Oriented Programming,
      Dynamic Programming,
      Data Structures,
      Computer Architecture
    }
  \headend


%-----------EXPERIENCE-----------------
\section{Experience}
  \headstart
  \titleplacehead
  {CyphaLab}{Remote}
    \roletimehead
      {Portfolio Manager}{April 2024 - Present}
      \itemstart
        \listitem{
          Spearheaded the development and optimization of the proprietary algorithmic trading
          portfolio for the company's cryptocurrency fund of \$500,000.
        }
        \listitem{
          Engineered and implemented a comprehensive suite of CTA strategies utilizing machine
          learning models such as LSTM, ARIMA, GBDT with Pytorch, Statsmodels, and XGBoost for
          effective reinvestment of corporate capital.
        }
        \listitem{
          Leveraged sophisticated optimization methodologies, including mean-variance, Calmar ratio,
          Kelly criterion, and expected shortfall, to enhance portfolio performance.
        }
        \listitem{
          Applied elastic regularization and principal component analysis (PCA) for dimensionality
          reduction, ensuring model robustness and mitigating overfitting.
        }
        \listitem{
          Achieved an annual Sharpe ratio of 3.49 and an annual Calmar ratio of 13.8 since
          inception.
        }
      \itemend
    \roletimehead
      {Data Scientist}{Januaray 2024 - April 2024}
      \itemstart
        \listitem{
          Ensembled CodeBERT and gradient boosting decision trees using Pytorch and XGBoost to
          classify malicious Ethereum smart contracts, achieving 0.89 F1 score on the test set.
        }
        \listitem{
          Built a transaction optimizer with Python to dynamically calculate the optimal gas price
          for Ethereum transactions and routing them through the optimal MEV relayer, reducing
          gas fees by 30\%.
        }
        \listitem{
          Built a data relayer hosted on Google Cloud Virtual Machine to provide on-chain DEX
          transaction data for online time series forecasting.
        }
      \itemend
      

    \titleplacehead
    {UC Berkeley Department of Mathematics}{Berkeley, CA}
      \roletimehead
        {Undergraduate Researcher - Stake-governed Random Turn Games}{August 2023 - Present}
        \itemstart
          \listitem{
            Built a finite integer line tug-of-war game simulator with Python, Numpy, and Pandas to 
            solve for Markov perfect equilibria with dynamic programming, and visualized the 
            results with Matplotlib.
          }
          \listitem{
            Constructed a computer assisted proof for the sufficient and necessary condition for
            the existence of a Markov perfect equilibrium in infinite integer line tug-of-war games, 
            being that the reward ratio is bounded within a $1\times10^{-4}$ interval from a symmetric 
            game: paper is currently under review.
          }
          \listitem{
            Reduced the run-time of the computer-assisted proof by from 3 hours to 20 minutes
            through the implementation of dynamic programming and vectorization techniques.
          }
        \itemend
        
      \roletimehead
        {Undergraduate Researcher - Mechanistic Interpretability}{September 2023 - December 2023}
        \itemstart
          \listitem{
            Reverse engineered Stockfish's efficiently updatable neural network's learned algorithm 
            using Pytorch, Sklearn, and Seaborn, achieving MSE of 1.8 compared to a simple linear 
            regression model with MSE of 126.
          }
          \listitem{
            Applied dimension reduction techniques such as SVD, neuron pruning, and feature 
            projection onto ReLU privileged basis to reverse engineer the embedding layer, showing 
            that each neuron's activation space is 95\%+ correlated.
          }
          \listitem{
            Aggregated 38GB training dataset with Sqlite and used Git for version 
            control.
          }
          \listitem{
            Built an Alpha-beta pruning algorithm \& NN based chess engine with C++ to 
            study the effect of neural network based evaluation functions on the performance of the 
            algorithm.
          }
        \itemend
      \vspace{5pt}

    \titleplacehead
      {UC Berkeley Department of EECS}{Berkeley, CA}
      \roletimehead{Academic Tutor - CS61A}{August 2023 - December 2023}
        \itemstart
          \listitem{
            Tutored students in Functional Programming, Object Oriented Programming, 
            and Dynamic Programming with Python in lab sessions.
          }
          \listitem{
            Held weekly office hours to help students with homework and projects, and tutored 
            other tutors.
          }
        \itemend

    \titleplacehead
      {HKUST School of Engineering}{Remote, CA}
      \roletimehead{Undergraduate Researcher - Machine Learning}{March 2023 - July 2023}
        \itemstart
          \listitem{
            Scraped and cleaned online data on the US economy and stock market using Python,
            BeautifulSoup, Selenium and Pandas, and stored mass data with MySQL.
          }
          \listitem{
            Analyzed economic indicators such as CPI and interest rate with regression and
            clustering using Numpy and Scikit-learn.
          }
          \listitem{
            Surveyed and summarized academic papers on state-of-the-art machine learning topics such
            as diffusion models for generative AI.
          }
        \itemend
  \headend


%-----------PROJECTS-----------------
% \section{Projects}
%   \headstart
%     \titletimehead{Mathematical Error Analysis Library}{December 2023 - Present}
%       \itemstart
%         \listitem{
%           Building a Numpy-like Python library to perform arithmetic
%           operations object-orientedly with associated error bounds factoring in floating point 
%           error.
%         }
%         \listitem{
%           Can be used in rigorous computer assisted proofs to bound the error of the results of
%           mathematical expressions.
%         }
%       \itemend
    
%     \titletimehead{2D Tile-based World Exploration Engine}{November 2023 (2 days)}
%       \itemstart
%         \listitem{
%           Built a 2D tile-based world exploration engine with \textbf{Java} that generates a random world 
%           with rooms and corridors, which allows the user to explore the world with a character, 
%           and was showcased for class project demo with an A+.
%         }
%         \listitem{
%           Implemented the A* search algorithm to find the shortest path between two points in the 
%           world and a snake game.
%         }
%       \itemend

%     \titletimehead{Trading Bot}{June 2023 - August 2023}
%       \itemstart
%         \listitem{
%           Implemented machine learning models with \textbf{Pytorch, Statsmodels, and XGBoost} for 
%           crypto price forecasting, e.g. LSTM, ARIMA, ETS Smoothing, Multi-linear Regression, 
%           GBRF, Sentiment Analysis, Transformer.
%         }
%         \listitem{
%           Built a trading bot with Python to trade cryptocurrency on Bybit using the Bybit API, 
%           achieving 1.98 Sharpe Ratio on the past 3 years of data by performing time series 
%           cross validation and features engineering.
%         }
%       \itemend

%     \titletimehead{Interview Questions Scraper}{April 2023 (1 hour)}
%       \itemstart
%         \listitem{
%           Built a web scraper with \textbf{Selenium} to scrape interview questions from 
%           Glassdoor.
%         }
%       \itemend
%   \headend

\end{document}
