%-------------------------
% Resume in Latex
% Based off of : https://github.com/sb2nov/resume/
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\input{preamble.tex}
\input{macros.tex}

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{{\LARGE Neo Lee}} \\
  \href{mailto:neo.lky852@gmail.com}{neo.lky852@gmail.com} $\vert$
  \href{tel:+12137130311}{(213) 713-0311} $\vert$
  \href{https://github.com/moneybabe}{github.com/moneybabe}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \headstart
    \titleplacehead
      {University of California, Berkeley}{GPA: 4.0/4.0}
    \roletimehead
      {Bachelor of Arts, Applied Mathematics, Computer Science}{Graduation: Spring 2026}
    \vspace{2pt}
    \listitem{Cal Alumni Leadership Scholarship}
    \vspace{5pt}
    \itemdesc{Relevant Coursework}{
      Machine Learning,
      Deep Learning,
      Optimization Theory,
      Time Series Analysis,
      Stochastic Process,
      Probability Theory,
      Linear Algebra,
      Discrete Mathematics,
      Graph Theory,
      Real Analysis,
      Numerical Analysis,
      Cryptography,
      Data Structures and Algorithms,
      Functional Programming,
      Object Oriented Programming,
      Dynamic Programming
    }
  \headend

  
%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
  \headstart
    \itemdesc{Languages}{
      Cantonese, Mandarin, English, Python, Java, SQL, MATLAB, R, Javascript, HTML, CSS, \LaTeX
    }
    \itemdesc{Tools}{
      Pytorch, Sklearn, *Boost*, Statsmodels, Pandas, Numpy, Seaborn, Plotly, Matplotlib, MySQL,
      Selenium, BeautifulSoup, Web3.py, Gcloud SDK, Docker, Git, Bash, Notion
    }
  \headend


%-----------EXPERIENCE-----------------
\section{Experience}
  \headstart
  \titleplacehead
  {CyphaLab}{Hong Kong / Remote}
    \roletimehead
      {Trading Intern}{April 2024 - Present}
      \itemstart
        \listitem{
          Assisted the development of the algorithmic trading division with a proprietary fund of
          \$500,000.
        }
        \listitem{
          Implemented a comprehensive suite of market neutral strategies utilizing machine learning
          models such as LSTM, ARIMA, GBDT with Pytorch, Statsmodels, and XGBoost, achieving an
          annual Sharpe ratio of 3.49 and an annual Calmar ratio of 7.2 in forward testing.
        }
        \listitem{
          Leveraged optimization methodologies, including mean-variance, Calmar ratio, Kelly
          criterion, and expected shortfall, to enhance portfolio performance.
        }
        \listitem{
          Developed an internal order tracking system with Python accompanied by a dashboard with
          Plotly to monitor the performance of the trading strategies across multiple exchanges
          in real time.
        }
        \listitem{
          Adopted Gitflow workflow for version control across the team.
        }
      \itemend


    \titleplacehead
    {UC Berkeley Department of Mathematics}{Berkeley, CA}
      \roletimehead
        {Undergraduate Researcher - Stake-governed Random Turn Games}{August 2023 - Present}
        \itemstart
          \listitem{
            Built a finite integer line tug-of-war game simulator with Python, Numpy, and Pandas to 
            solve for Markov perfect equilibria with dynamic programming, and visualized the 
            results with Matplotlib.
          }
          \listitem{
            Constructed a computer assisted proof utilizing interval arithmetic for the sufficient
            and necessary condition for the existence of a Markov perfect equilibrium in infinite
            integer line tug-of-war games, being that the reward ratio is bounded within a
            $1\times10^{-4}$ interval from a symmetric game: paper is currently under review.
          }
          \listitem{
            Reduced the run-time of the computer-assisted proof by from 3 hours to 20 minutes
            through the implementation of dynamic programming and vectorization techniques.
          }
        \itemend
        
        \roletimehead
        {Undergraduate Researcher - Mechanistic Interpretability}{September 2023 - Present}
        \itemstart
          \listitem{
            Reverse engineered Stockfish's efficiently updatable neural network's learned algorithm 
            using Pytorch, Sklearn, and Seaborn, achieving MSE of 1.8 compared to a simple linear 
            regression model with MSE of 126.
          }
          \listitem{
            Applied feature visualization techniques such as activation maximization, gradient
            ascent, and occlusion sensitivity to interpret the learned algorithm, showing that the
            neural network has learned to evaluate chess positions based on piece mobility and 
            piece value.
          }
          \listitem{
            Applied dimension reduction techniques such as SVD, neuron pruning, and feature 
            projection onto ReLU privileged basis to reverse engineer the embedding layer, showing 
            that each neuron's activation space is 95\%+ correlated.
          }
          \listitem{
            Aggregated 38GB training dataset with Sqlite and used Git for version 
            control.
          }
        \itemend

  \titleplacehead
  {UC Berkeley Department of EECS}{Berkeley, CA}
  \roletimehead{Academic Tutor - CS61A}{August 2023 - December 2023}
    \itemstart
      \listitem{
        Tutored students in Functional Programming, Object Oriented Programming, 
        and Dynamic Programming with Python in lab sessions.
      }
      \listitem{
        Held weekly office hours to help students with homework and projects, and tutored 
        other tutors.
      }
    \itemend

  \headend


% -----------PROJECTS-----------------
% \section{Projects}
%   \headstart
%     \titletimehead{Trading Bot}{June 2023 - August 2023}
%       \itemstart
%         \listitem{
%           Implemented machine learning models with Pytorch, Statsmodels, and XGBoost for 
%           crypto price forecasting, e.g. LSTM, ARIMA, ETS Smoothing, Multi-linear Regression, 
%           GBDT, BERT.
%         }
%         \listitem{
%           Built a trading bot with Python to trade cryptocurrency on Bybit using the Bybit API,
%           achieving 2.98 Sharpe Ratio on the test set by performing time series cross validation and
%           features engineering.
%         }
%       \itemend
%   \headend

\end{document}
